---
title: " "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### a little about me...
hi, i'm nicole (she/her), currently an undergrad studying computer science and data science at smith college. i'm a problem solving enthusiast. besides all these techy stuff, i love taylor swift🎶, singing🎙, and reading📖.

***
#### currently working on...
+ getting my bachelor degree in computer science and statistical & data science from Smith College, MA
+ learning C
+ developing my understanding of R

*** 
#### where i'm from...
i was born in manila, philippines, but spent a large part of my childhood in the island of bato, catanduanes before moving to the united states. 

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(sf)
library(maps)

# USA specific data
library(USAboundaries)
library(tidycensus)
library(tmaptools)
```

```{r , echo = FALSE}
philippines_cities <- tibble(
  name = c("Bato", "Manila"), 
  lat = c(13.6069, 14.5995), 
  lon = c(124.3199, 120.9842)
)

# Load maps package map object of US states and plot using default R plot
world_map <-  maps::map("world", plot = FALSE, fill = TRUE)

# Convert maps package map object to sf object using st_as_sf() again:
world_sf <- world_map %>% 
  st_as_sf(crs = 4326)

philippines_cities_sf <- philippines_cities %>% 
  st_as_sf(coords = c("lon", "lat"), crs = 4326)


# Convert maps package map object to sf object using st_as_sf() again & filter to ph:
philippines_sf <- world_sf %>% 
  filter(ID == "Philippines")


# Plot both layers:
ggplot() +
  geom_sf(data = philippines_sf) +
  geom_sf(data = philippines_cities_sf, aes(col = name), size = 3) +
  scale_color_manual(values=c("#751AD1","#3399FF")) +
  labs(title = "the philippines", col = "cities") +
  theme(panel.background = element_rect(fill = "aliceblue"))
```

***
#### call me, beep me if you wanna reach me...
feel free to reach me [by email](nicoletresvalles01@gmail.com), or any of my socials!
